Efficient Community Formation \\ for Web Services

### 2014-05-20 papers/coalition-journal-R1/coalition_journal_r1-final.tex
changes

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{s2_task_done.eps}
\includegraphics[width=3in]{s2_task_qos.eps}
\caption{Part (a): Cumulative number of tasks successfully done.
Part (b): Average QoS of tasks performed.} \label{performancemany}
\end{figure*}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{avg_task_ws_done.eps}
\includegraphics[width=3in]{avg_qos_ws_done.eps}
\includegraphics[width=3in]{avg_avail_ws_done.eps}
\caption{A comparison between our community model and the High
Availability Coalition model from \cite{10.1109/TSC.2012.12}. Part
(a): Cumulative number of tasks successfully done. Part (b):
Average QoS of tasks performed. Part (c): Average community
service availability} \label{fig_avail_method}
\end{figure*}

>>>>

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=1.5in]{s2_task_done.eps}
\includegraphics[width=1.5in]{s2_task_qos.eps}
\caption{Part (a): Cumulative number of tasks successfully done.
Part (b): Average QoS of tasks performed.} \label{performancemany}
\end{figure*}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=1.3in]{avg_task_ws_done.eps}
\includegraphics[width=1.3in]{avg_qos_ws_done.eps}
\includegraphics[width=1.3in]{avg_avail_ws_done.eps}
\caption{A comparison between our community model and the High
Availability Coalition model from \cite{10.1109/TSC.2012.12}. Part
(a): Cumulative number of tasks successfully done. Part (b):
Average QoS of tasks performed. Part (c): Average community
service availability} \label{fig_avail_method}
\end{figure*}
